Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-23 paper/paper.Rmd
edited, shortened leave-one-dist-out section

Spatial leave-one-out methods use individual observations in space as test partitions and apply circular buffer or guard zones around around these test points to enforce a minimum prediction distance. 
Leave-one-disc-out resampling modifies this approach to leave out circular regions centered at observation points. 
Note that this straightforward extension of the LOO method does technically not establish a partitioning as used for CV resampling in the traditional sense.

@@

Leave-one-disc-out resampling from package \pkg{sperrorest} randomly selects a circular test set starting from a single observations and optionally excludes a buffer zone from the remaining training data.
It thus ensures that a minimum separation distance between training and test data is maintained.
Discs are centered at sample locations, their number being specified by the `folds` argument.
It is therefore possible to sample up to $n$ discs without replacement (default) or any number when sampling with replacement (`replace = TRUE`).
The number of discs is specified via the `folds` argument.

This resampling method is, strictly speaking, not a partitioning method since the discs are not resulting in disjoint partitions - partitions will potentially overlap in subsequent folds.
Nevertheless, it is a logical extension of spatial LOO CV.
Depending on the size of the discs, potentially a large number of discs (`folds` argument) is needed to effectively use the entire dataset.

Even though the buffer creates a circular area which defines the test partition, it is not categorized as a "geometric" method as the origin of the circle is observation-based.
In contrast, "geometric" methods do not take into account single observation locations but only focus on the study area extend and will include all observations which fall into their respective covered area.

Leave-one-disc-out resampling becomes spatial LOO CV for a radius of 0 m and when each observation is at a unique location.

>>>>

Spatial leave-one-out methods use individual observations in space as test partitions and apply circular buffer or guard zones around around these test points to enforce a minimum prediction distance. 
Leave-one-disc-out resampling modifies this approach to leave out circular regions centered at observation points.

@@

Leave-one-disc-out resampling from package \pkg{sperrorest} defines circular test sets that are centered at sample locations, and optionally excludes a buffer zone from the remaining training data.
It thus ensures that a minimum separation distance between training and test data is maintained.
The number of discs is specified by the `folds` argument, which defaults to the sample size $n$.
Sample locations are selected randomly when `folds` is smaller than $n$; it is optionally possible to sample with replacement (`replace = TRUE`).
Leave-one-disc-out resampling becomes spatial LOO CV for a radius of 0 m and when each observation is at a unique location.

Note that the resampled discs will potentially overlap.
Strictly speaking, this straightforward extension of spatial LOO does therefore not establish a disjoint partitioning as used for CV resampling in the traditional sense.

<!-- AB: I don't think the following explanation is needed: -->
<!--
Even though the buffer creates a circular area which defines the test partition, it is not categorized as a "geometric" method as the origin of the circle is observation-based.
In contrast, "geometric" methods do not take into account single observation locations but only focus on the study area extend and will include all observations which fall into their respective covered area.
-->
